\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-01-12 doc/publications/plos16/plos16.tex
Change to better hyphen
changes to plos16.tex

\marginpar{signal rather than ``significant variables''}

@@

We note several things here:
\begin{itemize}
\item 
\end{itemize}

@@

\begin{figure}[tbhp] 
 \begin{adjustwidth}{-1.00in}{0in}
    \centering
    \includegraphics[totalheight=6cm]{./figs/phase-diagram-equivalence.png} 
    \caption{{\bf The phase chage diagram.}}
    \label{figure:phase-diagram-equivalence.png} 
    \vspace{4ex}
  \end{adjustwidth}
\end{figure}

\section{not for the paper}
Notes:
\begin{itemize}
\item we try a small simulation, a regression problem with $\beta(1:k) \sim U(1,100)$ and $y= X\beta + \epsilon$, $\epsilon \sim  N(0,\sqrt{16})$
\item \cite{Donoho.and.Stodden.2006} evaluate variable selection by 
$$\frac{\Vert\hat{\beta}-\beta\Vert_2}{\Vert\beta\Vert_2}$$
See figure \ref{figure:stepwise_lars_cv.png} 
\item 
However there is no $\hat{\beta}$ in a tree model. We are using variable importance as
a measure of the ordering of $\hat{\beta}$ (i.e. we expect variable importance to be proportional to $\hat{\beta}$). Is this correct?
\item as RF is sort of greedy approximation to combinatorial approach, it may have some success in the dead zone
\item  \cite{Donoho.and.Stodden.2006} are considering problems with $L_2$ errors (with additional  $L_1$ norms on the
  $\beta$. $L_1$).
How will their results carry over to 0-1 loss?
\end{itemize}

\begin{figure}[tbhp] 
  \begin{adjustwidth}{-1.00in}{0in}
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[totalheight=6cm]{./figs/k.png}
      \caption{k}
      \label{figure:k.png}
      \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[totalheight=6cm]{./figs/n.png}
      \caption{n}
      \label{figure:n.png}
    \end{subfigure} 
    \caption{}
  \end{adjustwidth}
\end{figure}

\begin{figure}[tbhp] 
  \begin{adjustwidth}{-1.00in}{0in}
    \begin{subfigure}[t]{0.5\linewidth}
      \centering
      \includegraphics[totalheight=6cm]{./figs/stepwise_lars_cv.png}
      \caption{Stepwise lars. $p=200$, $n$ and $k$ variable. Model selected by cross-validation}
      \label{figure:stepwise_lars_cv.png}
      \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[t]{0.5\linewidth}
      \centering
      \includegraphics[totalheight=6cm]{./figs/ranger.png}
      \caption{ranger, RBO}
      \label{figure:ranger.png}
    \end{subfigure} 
    \caption{}
  \end{adjustwidth}
\end{figure}

>>>>

@@

We note several things here:
\begin{itemize}
\item the Donoho-Tanner phase transition (in this setting) refers to estimating the $\beta$ in data generated by a
  linear model;
\item in a decision tree (random forest) there is no notion of estimating the $\beta$
\item also a decision tree (random forest) is a heruistic search. It may recover a relationshipin the space
  of the combinatorial search.
\end{itemize}

@@

\begin{figure}[tbhp] 
 \begin{adjustwidth}{-1.00in}{0in}
    \centering
    \includegraphics[totalheight=6cm]{./figs/phase.png} 
    \caption{{\bf The phase chage diagram.}}
    \label{figure:phase-diagram-equivalence.png} 
    \vspace{4ex}
  \end{adjustwidth}
\end{figure}
